Supplementary Information

### 2021-08-02 doc/manuscript/ForestGEO_treerings_SI.Rmd
add first draft of summary figure
#136
add plot of year trends for all growth metrics to SI
#141

@@

@@

![`r RW_interactions_all_legend` Shown are modeled response functions for species at the minimum and maximum and maximum ends of the DBH range. Other terms in the model are held constant at their medians. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate driver over the analysis period; shading indicates 1 SD. Species are color coded as in Figure 5.](tables_figures/pre_temp_groups_dbh_interactions_log_core_measurement_dbh.png){ width=90% }

>>>>

year_trends_all= "S16"

@@

year_trends_all_legend= "Figure S16. Year responses for all growth metrics."

@@

![`r RW_interactions_all_legend` Shown are modeled response functions for species at the minimum and maximum and maximum ends of the DBH range. Other terms in the model are held constant at their medians. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate driver over the analysis period; shading indicates 1 SD. Species are color coded as in Figure 6.](tables_figures/pre_temp_groups_dbh_interactions_log_core_measurement_dbh.png){ width=90% }

## `r year_trends_all_legend`

![`r year_trends_all_legend` For each species (color coded as in Figure 6), relationships are plotted if the year effect could be analyzed and was included in the top model. Other terms in the model are held constant at their medians. Best-fit polynomials are plotted with solid lines when both first- and second-order terms are significant (t-test’s p-value <0.05), dash-dotted lines when only one term is significant, and dotted lines when neither is significant.  Transparent ribbons indicate 95% confidence intervals. ](tables_figures/Year_responses.png){ width=75% }
